Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/relatedwork.tex
relwork

Weak consistency and high availability have been well
studied. Serializability has long been known to be
unachievable~\cite{davidson-survey} and Brewer's CAP Theorem has
attracted considerable attention~\cite{gilbert-cap}. The research has
begun to offer hints regarding the connection between ``weak
consistency'' and low latency~\cite{abadi-pacelc}, while several
studies examine weak isolation guarantees~\cite{adya,
  ansicritique}. However, as we have discussed, the connection between
weak consistency models in a distributed setting~\cite{calm, crdt} and
high availability is relatively unexplored. With the exception of a
preliminary workshop paper introducing HATs~\cite{hat-hotos}--- which
this work expands, providing impossibility results, a full
taxonomization, and experimental and application analysis (basically
all but Section 4.1)---we believe this paper is the first to explore
this area. Nonetheless, several studies rigorously classify non-HAT
semantics: Wisemann et al. have proposed a three parameter
classification for one-copy serializable database systems, performing
a more extensive classification than our overview in
Section~\ref{sec:evaluation}, including eager database replication
techniques~\cite{kemme-classification}. Additionally several earlier
surveys discuss distributed mechanisms for achieving one-copy
serializability~\cite{wisemann-survey}, linearizability, consistent
snapshots, and recency bounds~\cite{ceri-mechanism, chen-mechanism}.

>>>>

Weak consistency and high availability have been well
studied. Serializability has long been known to be
unachievable~\cite{davidson-survey} and Brewer's CAP Theorem has
attracted considerable attention~\cite{gilbert-cap}. The research has
begun to offer hints regarding the connection between ``weak
consistency'' and low latency~\cite{abadi-pacelc}, while several
studies examine weak isolation guarantees~\cite{adya,
  ansicritique}. However, as we have discussed, the connection between
weak consistency models in a distributed setting~\cite{calm, crdt} and
high availability is relatively unexplored. With the exception of a
preliminary workshop paper introducing HATs~\cite{hat-hotos}--- which
this work expands, providing impossibility results, a full
taxonomization, and experimental and application analysis---we believe
this paper is the first to explore this area. Nonetheless, several
studies rigorously classify non-HAT semantics: Wisemann et al. have
proposed a three parameter classification for one-copy serializable
database systems, performing a more extensive classification than our
overview in Section~\ref{sec:evaluation}, including eager database
replication techniques~\cite{kemme-classification}. Additionally
several earlier surveys discuss distributed mechanisms for achieving
one-copy serializability~\cite{wisemann-survey}, linearizability,
consistent snapshots, and recency bounds~\cite{ceri-mechanism,
  chen-mechanism}.
